---
title: "Feature Engineering for Improving Learning Environments: Week 1"
output: html_document
---
# Introudction
## Driving questions
1. What are the files that I have to work with?
2. Do these files meet my expectations?

## Where is your data?
When working with data, it is helpful to keep everything in one place. In my home directory, I created a folder called "Data" and in that folder I created a folder "OULAD."

For for information on importing and exporting data using R see <http://r4ds.had.co.nz/data-import.html#data-import>.

## Overview of datasets
Below, are the files and descriptions from OULAD:
(https://analyse.kmi.open.ac.uk/open_dataset#data)

* **assessments.csv:** This file contains information about assessments. Usually, every presentation has a number of assessments followed by the final exam.
* **courses.csv:** File contains the list of all available modules and their presentations.
* **studentAssessment.csv:** This file contains the results of students’ assessments. If the student does not submit the assessment, no result is recorded. The final exam submissions is missing, if the result of the assessments is not stored in the system.
* **studentInfo.csv:** This file contains demographic information about the students together with their results.
* **studentRegistration.csv:** This file contains information about the time when the student registered for the module presentation. For students who unregistered the date of unregistration is also recorded. 
* **studentVle.csv:** The studentVle.csv file contains information about each student’s interactions with the materials in the VLE.
* **vle.csv:** The csv file contains information about the available materials in the VLE. Typically these are html pages, pdf files, etc. Students have access to these materials online and their interactions with the materials are recorded.

```{r}
# Load packages
#install.packages("tidyverse")
#install.packages("skimr")
library(tidyverse)
library(skimr)
```
## assessments.csv
* **code_module:** identification code of the module, to which the assessment belongs.
* **code_presentation:** identification code of the presentation, to which the assessment belongs.
* **id_assessment:** identification number of the assessment.
* **assessment_type:** type of assessment. Three types of assessments exist: Tutor Marked Assessment (TMA), Computer Marked Assessment (CMA) and Final Exam (Exam).
* **date:** information about the final submission date of the assessment calculated as the number of days since the start of the module-presentation. The starting date of the presentation has number 0 (zero).
* **weight:** weight of the assessment in %. Typically, Exams are treated separately and have the weight 100%; the sum of all other assessments is 100%.

```{r}
assessments <- read_csv("~/Data/OULAD/assessments.csv")
```

```{r}
skim(assessments)
```


## courses.csv
* **code_module:** code name of the module, which serves as the identifier.
* **code_presentation:** code name of the presentation. It consists of the year and “B” for the presentation starting in February and “J” for the presentation starting in October.
* **length:** length of the module-presentation in days.

```{r}
courses <- read_csv("~/Data/OULAD/courses.csv")
```

```{r}
skim(courses)
```

## studentAssessment.csv
* **id_assessment:** the identification number of the assessment.
* **id_student:** a unique identification number for the student.
* **date_submitted:** the date of student submission, measured as the number of days since the start of the module presentation.
* **is_banked:** a status flag indicating that the assessment result has been transferred from a previous presentation.
* **score:** the student’s score in this assessment. The range is from 0 to 100. The score lower than 40 is interpreted as Fail. The marks are in the range from 0 to 100.

```{r}
stdas <- read_csv("~/Data/OULAD/studentAssessment.csv")
```

```{r}
skim(stdas)
```

## studentInfo.csv
* **code_module:** an identification code for a module on which the student is registered.
* **code_presentation:** the identification code of the presentation during which the student is registered on the module.
* **id_student:** a unique identification number for the student.
* **gender:** the student’s gender.
* **region:** identifies the geographic region, where the student lived while taking the module-presentation.
* **highest_education:** highest student education level on entry to the module presentation.
* **imd_band:** specifies the Index of Multiple Depravation band of the place where the student lived during the module-presentation.
* **age_band:** band of the student’s age.
* **num_of_prev_attempts:** the number times the student has attempted this module.
* **studied_credits:** the total number of credits for the modules the student is currently studying.
* **disability:** indicates whether the student has declared a disability.
* **final_result:** student’s final result in the module-presentation.

```{r}
stdinf <- read_csv("~/Data/OULAD/studentInfo.csv")
```

```{r}
skim(stdinf)
```

## studentRegistration.csv
* **code_module:** an identification code for a module.
* **code_presentation:** the identification code of the presentation.
* **id_student:** a unique identification number for the student.
* **date_registration:** the date of student’s registration on the module presentation, this is the number of days measured relative to the start of the module-presentation (e.g. the negative value -30 means that the student registered to module presentation 30 days before it started).
* **date_unregistration:** date of student unregistration from the module presentation, this is the number of days measured relative to the start of the module-presentation. Students, who completed the course have this field empty. Students who unregistered have Withdrawal as the value of the final_result column in the studentInfo.csv file.

```{r}
stdreg <- read_csv("~/Data/OULAD/studentRegistration.csv")
```

```{r}
skim(stdreg)
```

## studentVle.csv
Below are notes for the data elements contained in the "Student VLE" dataset.
* **code_module:** an identification code for a module.
* **code_presentation:** module presentation: year and section
* **id_student:** a unique student identifier
* **id_site:** an identification VLE material interacted with. (Important)
* **date:** when they interacted with VLE material
* **sum_click:** number of clicks per day (Somewhat problematic; would prefer each material click more granulary 
timestamped)

```{r}
stdvle <- read_csv("~/Data/OULAD/studentVle.csv")
```

```{r}
skim(stdvle)
```

## vle.csv
This file contains information related to each VLE activity.
* **id_site:** an identification number of the material.
* **code_module:** an identification code for module.
* **code_presentation:** the identification code of presentation.
* **activity_type:** the role associated with the module material.
* **week_from:** the week from which the material is planned to be used.
* **week_to:** week until which the material is planned to be used.

```{r}
vle <- read_csv("~/Data/OULAD/vle.csv")
```

```{r}
skim(vle)
```

