---
title: "Feature Engineering for Improving Learning Environments: Week 2"
output: html_document
---

# Part I

```{r}
# Load packages (suppress warning messages; not necessary)
#install.packages("tidyverse")
library(tidyverse)
```

```{r message=FALSE, warning=FALSE}
# Read in data from Week 1
assessments <- read_csv("~/Data/OULAD/assessments.csv")
courses <- read_csv("~/Data/OULAD/courses.csv")
stdas <- read_csv("~/Data/OULAD/studentAssessment.csv")
stdinf <- read_csv("~/Data/OULAD/studentInfo.csv")
stdreg <- read_csv("~/Data/OULAD/studentRegistration.csv")
stdvle <- read_csv("~/Data/OULAD/studentVle.csv")
vle <- read_csv("~/Data/OULAD/vle.csv")
```

## Begin subsetting data
```{r}
# Subset data to Module FFF
stdinf_f <- stdinf %>%
  filter(code_module == "FFF")
```

## Explore outcomes
```{r}
# Grade bar chart
stdinf_f %>%
  select(id_student, code_presentation, final_result) %>%
  unique() %>%
  ggplot(aes(x = final_result)) + 
  geom_bar() + 
  labs(x = "Final Result",
       y = "Number of Students") +
  facet_wrap(~code_presentation)
```

## Continue subsetting data
My demonstrations will be made using presentation "2013J."
For your assignments, please use presentation "2014J."
```{r}
# Subset studentInfo one step further: presentation 2013J
stdinf_f13j <- stdinf %>%
  filter(code_module == "FFF" & code_presentation == "2013J")
```

```{r}
# Subset VLE
stdvle_f13j <- stdvle %>%
  filter(code_module == "FFF" & code_presentation == "2013J")
```

```{r}
head(stdvle_f13j)
```

## Generate our first features
```{r}
# Create new data frame and the count of VLEs over tinme (VLE x Day)
# Count = VLE materials interacted with, could be duplicates
stdvle_f13j_ag <- stdvle_f13j %>%
  group_by(id_student) %>%
  summarise(total_vle = n(),
            unique_vle = n_distinct(id_site),
            total_clicks = sum(sum_click),
            days = n_distinct(date),
            unique_perday = unique_vle / days)
```

```{r}
head(stdvle_f13j_ag)
```

# Part II

## Visualizing distributions
```{r}
# Total VLE activities histogram
ggplot(stdvle_f13j_ag) +
           geom_histogram(aes(total_vle), binwidth = 100)
```

```{r}
# Total unique VLE activities
ggplot(stdvle_f13j_ag) +
           geom_histogram(aes(unique_vle), binwidth = 10)
```

```{r}
# Unique VLE activities per day
ggplot(stdvle_f13j_ag) +
           geom_histogram(aes(unique_perday), binwidth = .25)
```

## Joining data
```{r}
# Reduce variables inv the studentInf dataframe
stdinf_f13j_s <- stdinf_f13j %>%
  select(id_student, final_result)
```

```{r}
# Join studentIng and studentVle aggregated at student level
stdinf_f13j_s_vle_ag <- full_join(stdinf_f13j_s, stdvle_f13j_ag, by = "id_student")
```

## Explore covariation between outcome and predictor
```{r}
# Boxplot of final result and total unique VLE
stdinf_f13j_s_vle_ag %>%
  ggplot() +
  geom_boxplot(aes(x = final_result, y = unique_vle))
```

```{r}
# Boxplot of final result and unique VLE per day
stdinf_f13j_s_vle_ag %>%
  ggplot() +
  geom_boxplot(aes(x = final_result, y = unique_perday))
```

```{r}
# Boxplot of final result and days active
stdinf_f13j_s_vle_ag %>%
  ggplot() +
  geom_boxplot(aes(x = final_result, y = days))
```

```{r}
# Join student information with VLE activities
stdinf_f13j_s_vle <- full_join(stdinf_f13j_s, stdvle_f13j, by = "id_student")
```

```{r}
# What is the maximum date a student registered in the course?
stdinf_f13j_s_vle %>%
  group_by(id_student, final_result) %>%
  summarise(max_date = max(date)) %>%
  ggplot() +
  geom_boxplot(aes(x = final_result, y = max_date))
```

# Part III

## Working within a set timeframe
```{r}
# Explore total activity within specific timeframes
stdvle_f13j_ag50 <- stdvle_f13j %>%
  filter(date <= 50) %>% # modify as desired
  group_by(id_student) %>%
  summarise(total_vle = n(),
            unique_vle = n_distinct(id_site),
            total_clicks = sum(sum_click),
            days = n_distinct(date),
            unique_perday = unique_vle / days)

# Join new subsetted file with student final results
stdinf_f13j_s_vle_ag50 <- full_join(stdinf_f13j_s, stdvle_f13j_ag50, by = "id_student")

stdinf_f13j_s_vle_ag50 %>%
  ggplot() +
  geom_boxplot(aes(x = final_result, y = unique_vle))
```

## Cumulative activity
```{r}
# Visualize all observations
stdinf_f13j_s_vle %>%
    filter(date <= 50) %>%
    group_by(id_student, final_result, date) %>%
    summarise(total_per = n()) %>%
    arrange(id_student, date)%>%
    group_by(id_student) %>%
    mutate(cumul = cumsum(total_per)) %>%
    ggplot() +
        geom_jitter(aes(x = date, y = cumul, color = final_result), alpha = .2)
```

```{r}
# Visualize all observations using facetting
stdinf_f13j_s_vle %>%
    filter(date <= 50) %>%
    group_by(id_student, final_result, date) %>%
    summarise(unique_per = n()) %>%
    arrange(id_student, date)%>%
    group_by(id_student) %>%
    mutate(cumul = cumsum(unique_per)) %>%
    ggplot() +
        geom_jitter(aes(x = date, y = cumul, color = final_result), alpha = .2) + 
  facet_wrap(~final_result)
```

## Types of activities accessed
```{r}
# Identify most used VLE activities
most_used <- stdinf_f13j_s_vle %>%
  filter(date <= 50) %>%
  group_by(id_student, id_site, final_result) %>%
  unique() %>%
  summarise(total_per = n()) %>%
  group_by(id_site) %>%
  summarise(sum = sum(total_per)) 

most_used <- inner_join(most_used, vle, by = "id_site")

most_used %>%
  arrange(-sum)
```

## Relationship between student outcome and asessment scores
```{r}
# Join studentInf.csv subset and assessment studentAssessments.csv
stdinf_f13j_s_as <- inner_join(stdinf_f13j_s, stdas, by = "id_student")

stdinf_f13j_s_as <- left_join(stdinf_f13j_s_as, assessments, by = "id_assessment")

stdinf_f13j_s_as <- stdinf_f13j_s_as %>%
  filter(code_module == "FFF" & code_presentation == "2013J")
```

```{r}
# Generate count, mean, and standard deviations per assignment and final result
# Turned warning off because "score" column contains characters.
stdinf_f13j_s_as %>%
  group_by(final_result, assessment_type, id_assessment) %>%
  summarise(count = n(),
            mean_score = mean(score, na.rm = T),
            sd_score = sd(score, na.rm = T))
```

```{r}
# Remove question marks with NA
stdinf_f13j_s_as <- stdinf_f13j_s_as %>%
  mutate(score = ifelse(score == "?", NA, score),
         score = as.integer(score),
         date = as.integer(date))
```

```{r}
stdinf_f13j_s_as %>%
  group_by(final_result, assessment_type, id_assessment) %>%
  summarise(count = n(),
            mean_score = mean(score, na.rm = T),
            sd_score = sd(score, na.rm = T))
```

```{r}
# Add date to the way we are aggregrating means
stdinf_f13j_s_as %>%
  group_by(final_result, assessment_type, date, id_assessment) %>%
  summarise(count = n(),
            mean_score = mean(score, na.rm = T),
            sd_score = sd(score, na.rm = T)) %>%
  arrange(final_result, date)
```

```{r}
# Create boxplots to visually explore relationships
stdinf_f13j_s_as %>%
  mutate(date = as.numeric(date),
         score = as.numeric(ifelse(score == "?", NA, score))) %>%
  filter(date <= 100) %>% 
  ggplot() + 
  geom_boxplot(aes(x = as.factor(id_assessment), y = score, colour = final_result))
```
